%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Yisong Wang} \\ \vspace{1pt}
    \href{mailto:a123nce@gmail.com}{\underline{a123nce@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/zazkenti/}{\underline{linkedin.com/in/zazkenti/}} $|$
    \href{https://github.com/zazkenti}{\underline{github.com/zazkenti}} $|$ 
    \href{650-996-6311}{\underline{650-996-6311}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Independence High School}{San Jose, CA}
      {High School Diploma}{August 2020 - May 2024}
    \resumeSubheading
      {San Jose State University}{San Jose, CA}
      {Bachelor of Science in Computer Science}{Expected: May 2028}
      \begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
}}
\end{itemize}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Red Lobster}{July 2024 -- December 2024}
    {Server Assistant(Host/Busser/Runner)}{Milpitas, CA}
    \resumeItemListStart
      \resumeItem{Skilled in handling a variety of cleaning equipment, food running, and using the cashier or POS stations.}
      \resumeItem{Help create a welcoming customer experience for all and handle customer inquiries with confidence and honesty.}
      \resumeItem{Developed reliable communication skills among team members by actively communicating with the servers, cooks, and managers for the customers to have a steadfast experience.}
    \resumeItemListEnd

\resumeSubheading
  {HeyTea}{Jan. 2025 -- Mar. 2025}
  {Barista/Food Preparation}{Milpitas, CA}
  \resumeItemListStart
    \resumeItem{Demonstrated proficiency in operating various coffee machines and equipment, ensuring high-quality beverage preparation.}
    \resumeItem{Maintained a clean and organized workspace, adhering to health and safety standards while preparing and serving beverages.}
    \resumeItem{Developed expert teamwork skills by collaborating with colleagues to ensure efficient service and customer satisfaction.}
  \resumeItemListEnd

\resumeSubheading
  {Junior Achievement USA}{February 2024 -- May 2024}
  {Team Member}{San Jose, CA}
  \resumeItemListStart
    \resumeItem{Organized financial records for the student-led company, ensuring accuracy and transparency in financial transactions.}
    \resumeItem{Worked with students and teachers to develop a comprehensive business plan, including market research, product development, and financial projections.}
    \resumeItem{Secured and handled cash transactions, ensuring proper cash management and accountability.}
  \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------Awards-----------
\section{Awards}
    \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{\underline{\href{2024 CED X Hackathon Spartup Winner}{2024 CED X Hackathon Spartup Winner}}}} { }
      \resumeItemListStart
        \resumeItem{Helped research and prove the feasibility of a suagrcane-based water filtration system while incorpoating artificial intelligence for the 2024 CED X Hackathon Spartup event.}
      \resumeItemListEnd
      \resumeProjectHeading
      {\textbf{\underline{\href{2024 Seal of Biliteracy: Chinese}{2024 Seal of Biliteracy: Chinese}}}} { }
      \resumeItemListStart
        \resumeItem{Awarded the Seal of Biliteracy in Chinese for demonstrating proficiency in both English and Chinese languages, showcasing my bilingual capabilities.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------SKILLS-----------
\section{Core Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages Fluent}{: English, Mandarin} \\
     \textbf{Programming Languages}{: Java, Python, Javascript} \\
     \textbf{Developer Tools}{: Git, VS Code, PyCharm} \\
     \textbf{Certifications and Licenses}{: Class C Driver's License, Food Handler's Certifiction} \\
     \textbf{Other Skills}{: Cash Handling, Computer Skills, POS Experience, Customer Service, Teamwork, Time Management, Communication Skills} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}